Energy-Aware Planning-Scheduling for\\Autonomous Aerial Robots

### 2022-05-20 review/response-letter.tex

\begin{formal}
  \color{black} [...] this section details a [...] motion with a wide turning radius. It is similar to another motion in the literature, the Zamboni
  motion [{\color{green}40}], but additionally allows variable CPP [...] {\color{blue} Although cover variability is already considered in the literature [{\color{green}23}], it is limited to boustrophedon motion for rotary wings.} The novel motion is termed Zamboni-like motion [...]
  \vspace*{1ex}
\end{formal}

@@

- High-level comment: the paper would benefit from restructuring for clarity to better convey the interesting technical ideas. At present, difficult to understand the insights behind the main contributions. For example, ``the re-planning-scheduling problem is finding the optimal trajectory of parameters $c_i$ in time.'' -- optimal w.r.t. what objective function? Total energy? Mission duration? Make this clear in the problem definition section.

{\color{blue}

{\hspace*{-4.5em}{[R2:2]}\vspace*{-1.9em}}

Thank you for the high-level comment and for proposing to state clearly the objective function. Regarding the objective function, we have integrated the problem definition accordingly, whereas we have altered the text in the manuscript by both implementing the specific comments and rewriting some technical details or adding further commentary.

@@

  Also, ``The energy optimization of computations schedules can be achieved by, e.g., varying the quality of service between specific bounds [12] and frequency and voltage of the computing hardware [9], [13], [14]. We focus on the former aspect and schedule the onboard computations altering their quality while simultaneously changing the quality of the coverage'' --$>$ What are the actual computation inputs that can be changed? It is unclear throughout the paper what $c_i^\sigma$ is.

  {\color{blue}

  {\hspace*{-4.5em}{[R2:3]}\vspace*{-1.9em}}

  Thank you for underlying the need to state clearly what the computations parameters refer to. We have not realized this point was not stated explicitly earlier than in the experimental setup. Our purpose is to alter the granularity at which different computations run so that the energy consumption required by the computing hardware onboard the aerial robot increases or decreases.

@@

  {\color{blue}

  {\hspace*{-4.5em}{[R2:4]}\vspace*{-1.9em}}

  Thank you for noticing the comparison was missing in the manuscript. We utilize as a performance metric the weighted average configuration of parameters against the battery state of charge at the end of the flight. We have added explanatory text to the simulation results to report the metric for i and ii against I and II respectively.

  \begin{formal}
    {\color{blue}
Assuming both the parameters are weighted equally, and the initial battery SoC is seventy percent, {\color{red}I} would not be able to complete the flight, and {\color{red}II} has a performance metric of zero (i.e., the lowest configuration of parameters throughout the flight).
Nonetheless, performance metrics of {\color{red}i} and {\color{red}ii} are 13.05 and 2.24, whereas the average detection and coverage quality is approx. 45 and 35 percent for {\color{red}i}, and 62 and 87 percent for {\color{red}ii}.}  
    \vspace*{1ex}
  \end{formal}
  }

@@

- Paper would benefit from clear indication of what the performance metric we want to see improve.

{\color{blue}

{\hspace*{-4.5em}{[R2:5]}\vspace*{-1.9em}}

Thank you for suggesting adding a clear indication of what performance metric is being utilized. Indeed this information was missing in the original manuscript. We have added explanatory text in Problem Formulation to address the point.

\begin{formal}\color{black}
The problem %of planning-scheduling 
is {\color{blue}split into }%composed of 
two%sub-problems.
{\color{blue}: }%. One is 
to form a %static 
plan that visits every point in space {\color{blue}and }%the other to
re-plan and -schedule the plan in-flight in an energy-aware way. %{\color{blue}, whereas }
{\color{blue} 
The re-planning-scheduling improves the performance metric of quality of the plan and schedule against battery state of charge (SoC), i.e., the weighted average value of parameters divided by the remaining SoC.
%The performance metric the re-planning-scheduling %in the letter 
%improves is %then
%the quality of the plan-schedule against battery state of charge (SoC), e.g., weighted average value of parameters divided by remaining %battery 
%SoC.% at the end of the flight.
}
\vspace*{1ex}
\end{formal}
}

@@

{\hspace*{-4.5em}{[R2:7]}\vspace*{-1.9em}}

Thank you for underlying this point. We have not realized that it was not clear in the original manuscript. We use the concept of path parameters as inputs to the path functions that compose the coverage path to ultimately alter the coverage quality dynamically, throughout the flight.

We have added explanatory text to Section IV-A to make this point clear.

\begin{formal}
  \color{black}
  [...] It is similar to another motion in the literature, the \emph{Zamboni motion}~[{\color{green}40}], but additionally allows variable CPP %at the very core of this work
  {\color{blue} by dynamically altering the distance between the survey lines with the path parameters}. 
  {\color{blue} Although cover variability is already considered in the literature~[{\color{green}23}], it is limited to boustrophedon motion for rotary wings.}
  The novel motion is termed \emph{Zamboni-like motion} and is composed of four primitive paths (see Definition~{\color{red}II.5}): two lines $\varphi_1,\varphi_2$ and two circles $\varphi_3,\varphi_4$. [...]% (see Fig.~\ref{fig:zambo}).
  \vspace*{1ex}
\end{formal}
}

@@

{\color{blue}

{\hspace*{-4.5em}{[R2:10]}\vspace*{-1.9em}}

Thank you for underlying this possible source of confusion. We have fixed the text to clearly state whether the category is in the former or latter occurrence.

\begin{formal}
  \color{black} [...] There are other classes where planning-scheduling energy awareness leads to irrelevant savings, i.e., when the motion energy contribution far outreaches the computations or vice-versa. The {\color{blue}motion outreaching computation energy} frequently happens with rotary-wing aerial robots (e.g., quadrotors or quadcopters, hexacopters, etc.){\color{blue}, the opposite occurs with} lighter-than-air aerial robots (e.g., blimps). [...]
  \vspace*{1ex}
\end{formal}}

@@

- ordering of figures in Figure 6 is confusing. Consider lumping each case in a separate row (I, i, II, ii).

{\color{blue}

{\hspace*{-4.5em}{[R2:11]}\vspace*{-1.9em}}

Thank you for underlying the issue. We have attempted to optimize the space but overloaded the figure and significantly reduced its readability. We have reordered Figure 6 to address the issue. We have first split the figure into two figures, 6 and 7. In both, we utilize one row per case. Figure 6 contains cases I and II related to static coverage at the two boundary configurations under varying wind speeds and directions.

\begin{formal}
  \footnotesize
  \input{../figures/results/new_physics2/new_trajs-ener_I-II.tikz}
  {\color{blue}Fig.~6:~\color{blue}CPP with Zamboni-like motion using two boundary configurations. In {\color{red}a} are the trajectories of the coverage--the highest in {\color{red}I} and the lowest in {\color{red}II}. In {\color{red}b} are the energy and the period evolutions for both {\color{red}I} and {\color{red}II} with different atmospheric conditions. In {\color{red}c} are the states of the energy model for {\color{red}I}.}
\end{formal}
